Draft_spatio

### 2021-07-15 R/Draft_spatio.Rmd

#Taf de l'utilisateur

## Import du MNT de Paracou (1m de résolution, campagne LiDAR de 2016) ----
DemParacou <- raster::raster("D:/VSC Kourou/DATA/GIS/Topo_P6_PARACOU.tif") # MNT (altitude)
plot(DemParacou)

>>>>

#Taf de l'utilisateur
## Import du MNT de Paracou (1m de résolution, campagne LiDAR de 2016) ----
DemParacou <- raster::raster("D:/VSC Kourou/DATA/GIS/Topo_P6_PARACOU.tif") # MNT (altitude)
plot(DemParacou)
